Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-30 document/ms.tex

@@

@@

%
%  RULES OF THE GAME, MOTHAFUCKERS.
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ALWAYS cite inside parens () and use \citealt{}; no in-line cites
%  * that is all.
%

@@

@@

>>>>

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ALWAYS cite inside parens () and use \citealt{}; no in-line cites
%  * that is all.
%

@@

\include{vc}

@@

@@

\begin{figure}
\begin{center}
\includegraphics{figures/separable-radius.pdf}
\end{center}
\caption{%
The inferred distribution of exoplanet radii assuming a separable rate
function.
The black lines are draws from the posterior probability distribution of bin
heights and the red points are previous measurements based on the same
dataset (\citealt{petigura}).
\figlabel{separable-radius}}
\end{figure}

\section{General distribution}

It has been shown that the joint period--radius distribution for exoplanets is
not separable (\dfmtodo{CITE}).
In this section, we discuss non-separable model in our analysis framework.

We model the rate function $\rate(\period,\,\radius)$ as a piecewise constant
function in rectangular bins in $\ln\period$ and $\ln\radius$.
The parameters \ratepars\ that we're fitting are the values of each of these
bins (subject to a normalization constraint).

@@

All of the code used in this project is available from
\url{http://github.com/dfm/exopop} under the MIT open-source software license.
This code (plus some dependencies) can be run to re-generate all of the
figures and results in this \paper; this version of the paper was generated
with git commit \texttt{\githash} (\gitdate).
